---
title: "Dynamic Dashboard"
#author: "Mathias Dah Fienon"
output: 
  flexdashboard::flex_dashboard:
    theme: united
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(kableExtra)
library(DT)
library(ggplot2)
theme_set(new = theme_bw())
library(plotly)
library(shiny)
```

# Data

## {.sidebar data-width=250}

---

```{r}
selectInput(inputId = "var_displ",
                       label = "Species to display",
                       choices = levels(iris$Species),
                       selected = levels(iris$Species),
                       multiple = TRUE)
```

---

```{r}
data_display <- reactive({
  subset(iris, subset = Species %in% input$var_displ, )
})

ligne <- reactive({
  as.numeric(rownames(data_display()))
})

renderUI({
  rdtr <- range(ligne())
  sliderInput(inputId = "number_rows",
            label = "Rows to display",
            min = rdtr[1] ,
            max = rdtr[2],
            value =  rdtr,
            dragRange = FALSE)
})
```

---

## 
---
Observations: `r renderText(input$number_rows[1])` - `r renderText(input$number_rows[2])`   
<br>
Species: `r renderText(input$var_displ)`

<br>

---

```{r}
 
renderTable({
  req(input$number_rows)
  data_display()[ligne() %in% c(input$number_rows[1]:input$number_rows[2]),]},
  rownames = TRUE)
```




# Exploration

## {.sidebar data-width=150}

```{r}
selectInput(inputId = "x",
            label = "Pick an independent variable (X)",
            choices = names(iris)[sapply(iris, is.numeric)],
            selected = names(iris)[sapply(iris, is.numeric)][3])
```

---

```{r}
selectInput(inputId = "y",
            label = "Pick an independent variable (Y)",
            choices = names(iris)[sapply(iris, is.numeric)],
            selected = names(iris)[sapply(iris, is.numeric)][4])
```



## {.tabset data-width=350}

### Summaries

#### `r renderText({paste("Summary of",input$x, "by Species")})`

```{r}
renderTable({
  resx <- aggregate(get(input$x)~Species, iris, FUN = summary)[[2]]
  rownames(resx) <- levels(iris$Species)
  resx
},
digits = 2,
hover = TRUE,
rownames = TRUE)
```

---
#### `r renderText({paste("Summary of",input$y, "by Species")})`

```{r}
renderTable({
  resx <- aggregate(get(input$y)~Species, iris, FUN = summary)[[2]]
  rownames(resx) <- levels(iris$Species)
  resx
},
digits = 2,
hover = TRUE,
rownames = TRUE)
```


### Linear models

#### `r renderText({paste("lm:",input$y, "~", input$x)})`




_**`setosa`**_
```{r}
renderTable({
  m1 <- lm(get(input$y) ~ get(input$x), data = subset(iris, Species == "setosa"))
    m1 <- summary(m1)$coef
    row.names(m1) <- c("(Intercept)", input$x)
    m1
},
digits = 3,
hover = TRUE,
rownames = TRUE
)

```

_**`versicolor`**_
```{r}
renderTable({
  m1 <- lm(get(input$y) ~ get(input$x), data = subset(iris, Species == "versicolor"))
    m1 <- summary(m1)$coef
    row.names(m1) <- c("(Intercept)", input$x)
    m1
},
digits = 3,
hover = TRUE,
rownames = TRUE
)

```


_**`virginica`**_

```{r}
renderTable({
  m1 <- lm(get(input$y) ~ get(input$x), data = subset(iris, Species == "virginica"))
    m1 <- summary(m1)$coef
    row.names(m1) <- c("(Intercept)", input$x)
    m1
},
digits = 3,
hover = TRUE,
rownames = TRUE
)

```


## {.tabset data-width=500}

### Densities

```{r}
irisL <- cbind(
  Species = iris$Species,
  iris |> stack(select = -Species)
)
```

```{r}
renderPlotly({
  dt <- subset(irisL, ind %in% c(input$x, input$y))
  h <- ggplot(dt)+
    aes(x = values, fill = Species)+
    geom_density(alpha = 0.5)+
    labs(x = "", y = "Density")+
    facet_wrap(facets = vars(ind))
  
  ggplotly(h)
})
```


### Linear models

```{r}
renderPlotly({
  f <- ggplot(iris)+
  aes(x = get(input$x), y = get(input$y), col = Species)+
  geom_point()+
    labs(x=input$x, y=input$y)+
    geom_smooth(method = "lm")
ggplotly(f)
})
```





